Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Missing word.
Put "meek" in normal type.
Say that 28% of clients had 2 concurrent connections or fewer.

% Avoid line breaks in program names.
\newcommand{\meekclient}{\mbox{meek-client}\xspace}
\newcommand{\meekserver}{\mbox{meek-server}\xspace}
\newcommand{\meek}{\texttt{meek}\xspace}
\newcommand{\lbl}{ResearchLab\xspace}
\def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}

@@

% Output of concurrent.R.
% [1] 2745
% [1] 2.610621
% [1] 1
% [1] 1.002148

@@

The number of concurrent connections is another potential distinguisher.
We have seen how \meek\ tends to use one long-lived connection
through which it tunnels all its requests.
Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
Google per client in both traces.
The number of connections in the \lbl trace is variable,
with some hosts briefly spiking up above 50 connections,
but the average case is very heavily skewed to smaller numbers.
The average number of connections in the \lbl trace is 2.61,
while in the \meek\ trace it is almost exactly 1, only briefly
deviating when one connection ends and another begins.
We conclude that having a small number of concurrent connections is unremarkable.

% TODO: Since the average numbers of connections are quite different, reviewers may think
% it is remarkable. We should probably show a large percentage of users in the \lbl trace only
% have 1~2 connections throughout. Therefore a \meek\ user is a needle in the haystack.

@@

Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
Most users who use Tor, use it with Tor Browser~\cite{torbrowser},
a customized version of Firefox that is
preconfigured to use a built-in Tor client.
% and patched to defend against application-layer privacy and anonymity threats
% like tracking cookies and web browser fingerprinting.
Tor Browser has an easy interface for selecting pluggable transports.
We made a series experimental releases of Tor Browser featuring \meek,
releasing the first one on February~18.
[Some details of deployment are omitted for anonymous submission.]
% ANON
% On April~18 we made the first release featuring the browser camouflage
% that is the subject of Section~\ref{sec:browserextension}.
% We announced our releases on Tor development mailing lists,
% whence they were picked up by Tor Weekly News on the Tor blog.
% Our code was merged by the Tor Browser maintainers
% in June and is scheduled for an alpha release,
% still pending as of this writing.

>>>>

% Avoid line breaks in program names.
\newcommand{\meekclient}{\mbox{meek-client}\xspace}
\newcommand{\meekserver}{\mbox{meek-server}\xspace}
\newcommand{\meek}{meek\xspace}
\newcommand{\lbl}{ResearchLab\xspace}
\def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}

@@

% Output of concurrent.R.
% [1] 2745
% [1] 2.610621
% [1] 1
% [1] 1.002148
% [1] 772
% [1] 2745
% [1] 0.2812386

@@

The number of concurrent connections is another potential distinguisher.
We have seen how \meek\ tends to use one long-lived connection
through which it tunnels all its requests.
Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
Google per client in both traces.
The number of connections in the \lbl trace is variable,
with some hosts briefly spiking up above 50 connections,
but the average case is very heavily skewed to smaller numbers.
The average number of connections in the \lbl trace is 2.61,
with 28\% of clients never having more than 2 concurrent connections.
In the \meek trace the average is almost exactly 1, only briefly
deviating when one connection ends and another begins.
We conclude that having a small number of concurrent connections is unremarkable.

@@

Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
Most users who use Tor, use it with Tor Browser~\cite{torbrowser},
a customized version of Firefox that is
preconfigured to use a built-in Tor client.
% and patched to defend against application-layer privacy and anonymity threats
% like tracking cookies and web browser fingerprinting.
Tor Browser has an easy interface for selecting pluggable transports.
We made a series of experimental releases of Tor Browser featuring \meek,
releasing the first one on February~18.
[Some details of deployment are omitted for anonymous submission.]
% ANON
% On April~18 we made the first release featuring the browser camouflage
% that is the subject of Section~\ref{sec:browserextension}.
% We announced our releases on Tor development mailing lists,
% whence they were picked up by Tor Weekly News on the Tor blog.
% Our code was merged by the Tor Browser maintainers
% in June and is scheduled for an alpha release,
% still pending as of this writing.
